### 2019-04-16 papers/haskell19/4-generators.tex
Code refactor
Added file

\section{Generating Composable Data via Type-level Specfications}
\label{sec:generators}

@@

\begin{code}
type Con' a    = Term  (Con a)
type Fun' a    = Term  (Fun a)
type Pat' a n  = Term  (Pat a n)
\end{code}

\begin{code}
type HtmlSpec
  =      Con'  "Text"
  oplus  Con   "Join"         otimes 2
  oplus  Fun'  "br"           otimes 4
  oplus  Fun   "<+>"          otimes 9
  oplus  Pat   "simplify"  1  otimes 3
  oplus  Pat   "simplify"  2  otimes 5
\end{code}

>>>>

\section{Generating Random Constructions}
\label{sec:generators}

@@

### 2019-04-16 papers/haskell19/8-conclusions.tex
Added file

\section{Random Testing using Hints}
\label{sec:sources}

@@

\begin{code}
data Html
  =  Text  String
  |  Sing  String
  |  Tag   String Html
  |  Join  Html Html
\end{code}

A value of type |Html| represents either plain text strings, via the |Text| data
constructor; single and paired HTML tags using the |Sing| and |Tag| data
constructors, respectively; and concatenation of ...

\begin{code}
class Arbitrary (a :: *) where
  arbitrary :: Gen a
\end{code}

\begin{code}
class Arbitrary (a :: *) where
  arbitrary :: Gen a
\end{code}

\begin{code}
instance Arbitrary Html where
  arbitrary = sized gen
    where
      gen 0 = frequency
        [  (2,  Text    <$> arbitrary)
        ,  (1,  Single  <$> arbitrary) ]
      gen n = frequency
        [  (2,  Text    <$> arbitrary)
        ,  (1,  Single  <$> arbitrary)
        ,  (4,  Tag     <$> arbitrary  <*> gen (n-1))
        ,  (3,  Join    <$> gen (n-1)  <*> gen (n-1)) ]
\end{code} %$

\begin{code}
br :: Html
br = Sing "br"

bold :: Html -> Html
bold = Tag "b"

(<+>) :: Html -> Html -> Html
(<+>) x y = Join x (Join br y)

list :: [Html] -> Html
list xs = Tag "ul" (foldl1 Join (Tag "li" <$> xs))
\end{code} %$

\begin{code}
simplify :: Html -> Html
simplify (Join (Text t1) (Text t2))
  = Text (t1 ++ t2)
simplify (Join (Join (Text t1) x) y)
  = simplify (Join (Text t1) (simplify (Join x y)))
simplify (Join x y)
  = Join (simplify x) (simplify y)
simplify (Tag t x)
  = Tag t (simplify x)
simplify x = x
\end{code}

>>>>

\section{Conclusions}
\label{sec:conclusions}

@@
